Challenges on quantifying fish range shifts across management boundaries

### 2021-08-13 Scripts/manuscript_acrossboundaries.Rmd
included results

# Results
-	Two boundaries methods
-	Two surveys

>>>>

# Methods

We expanded the grid following two methods (Fig. 1).

![Figure 1. Spatial regions within the United States' North East Exclusive Economic Zone. A) Spatial buffers from each State's waters. B) Spatial buffers from the main fishing ports. States are aligned by average latitude from north to south. ME = Maine; NH, New Hampshire; MA, Massachusetts; RI, Rhode Island; CT, Connecticut; NY, New York; NY, New Jersey; DE, Delaware; MD, Maryland; VA Virginia; North Carolina.](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F1_buffer_figure.jpg)

# Results

![Figure 2. Change in the proportion of species distribution per State in recent years (2002 - 2014) relative to the reference years (1990-2001) following the fishing ports (top) and State waters (middle) approach. Bottom pannel showing the percentage difference between both approaches. ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F2_proportion_chg_diff.jpg)

![Figure 3. Aggregated distribution proportion per state of Paralichthys dentatus, Stenotomus chrysops and Centropristis striata over time. Each color represent a State ordered latitudinal. Grey box represents the base-period used for the fisheries quota allocation ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F3_area_plot_avg_agg_sptl.jpg)

![Figure 4. Proportion of the distribution of Paralichthys dentatus, Stenotomus chrysops and Centropristis striata over time. Each color represent a State ordered latitudinal. Grey box represents the base-period used for the fisheries quota allocation ](/Volumes/Enterprise/Data/AcrossBoundaries/Results/Figures/F4_area_plot_avg_spp_sptl.jpg)
